\textbf{Support for linking tests to application lifecycle management (ALM) repositories}
\begin{itemize}
\item You can now integrate your automated tests with external repositories which you have configured in your workspace and your \gdproject{}.
\item The integration lets you specify a task ID on items in your \gdproject{} -- most usually the task from an external system for which this test is relevant. 
\item You can open the task for a node from the browsers. 
\item When a test runs via the \ite{}, the test results from the test are attached to the relevant tasks in the external repository as a comment with a link which can be opened in the \dash{}.
\item It is not currently possible to decide on a per-test basis whether or not to report. If you do not want to report for a test, then you should remove the checkboxes for reporting from the \gdproject{} properties. 
\item \gdjobs{} currently do not report to external systems. 
\item We have tested the integration on Bugzilla and JIRA successfully. An integration with HP ALM is not possible in the current version. 
\end{itemize}

\textbf{New option in the testexec}
\begin{itemize}
\item The testexec has a new option in the command line (not in the configuration file).
\item Use the parameter \bxshell{-sx} to not write any screenshots to the HTML or XML files.
\end{itemize}

\textbf{Comments can be added to the \gdproject{} and to categories}
\begin{itemize}
\item You can now add comments to the \gdproject{} and to categories in the \gdtestsuitebrowser{} and \gdtestcasebrowser{}.
\end{itemize}

\textbf{New actions for testing checkboxes in SWT tables}
\begin{itemize}
\item Tables in SWT/RCP \gdauts{} that have a checkbox in the first column can now be tested.
\item There are actions to toggle the state of the checkbox, and to check the state of the checkbox.
\item The row to be checked is defined either by its selection or by the mouse position.
\end{itemize}

\textbf{Save As... option in image view}
\begin{itemize}
\item You can now save images from errors in the test directly to your file system  using a new button and the context menu in the image view.
\end{itemize}

\textbf{JProgress bar now supported as graphics component}
\begin{itemize}
\item You can now map JProgressBar components in Swing and SWT \gdauts{}.
\item The component is supported as a graphics component -- you can check its existence, wait for it etc.
\end{itemize}

\textbf{HTML: the <div> tag is supported as a component with text}
\begin{itemize}
\item You can now perform check text actions on components in HTML \gdauts{} that use the <div> tag.
\end{itemize}

\textbf{Changes to dashboard}
\begin{itemize}
\item The URL for the \dash{} has been shortened. 
\item The dashboard URL is now:
\begin{verbatim}
http://HOSTNAME:PORTNUMBER/dashboard
\end{verbatim}
\item The properties for the dashboard have also been renamed from \textit{com.bredexsw.guidancer} to \textit{org.eclipse.jubula}. Please ensure you update any properties files you use for the dashboard server.
\end{itemize}

\textbf{Next and previous error buttons in \gdtestresultview{} that appears during test execution}
\begin{itemize}
\item You can now also use the next and previous error buttons for the \gdtestresultview{} that appears during test execution.
\end{itemize}

\textbf{New test data functions}
There are new functions available in the \ite{}:
\begin{itemize}
\item randomInt(exclusive maximum value) -- to generate a random integer.
\item replaceAll(string,regular expression,replacement) -- to replace parts of a string with something else.
\item uuid() -- to generate a universal unique ID.
\item base64Encode(string) -- to encode a string to base64.
\item base64Decode(string) -- to decode a string from base64.
\end{itemize}
