
\index{Add!AUT Configuration}
\index{AUT Configuration!Add}
\index{Edit!AUT Configuration}
\index{AUT Configuration!Edit}
\index{AUT!Configuration}
\index{Configuration!AUT}
\index{Activation}
\index{Application activation}
\index{ID attribute name}
\index{AUT ID}

The \gdaut{} configuration dialog for HTML has three different levels of detail: basic, advanced and expert. 

See the sections below for information on the different levels. 

\subsubsection{Basic HTML \gdaut{} configuration}

Use the basic setting to specify the URL and Browser you wish to start this \gdaut{} configuration on. 

\begin{enumerate}
\item A suggested name for this \gdaut{} configuration is generated automatically based on your \gdaut{} name and the default \gdagent{} host. You can change this name if you wish. 
\item The default \gdagent host is also automatically selected. You can select a new \gdagent{} from the combo box or add a new one by clicking \bxcaption{New}. For more information on adding and editing an \gdagent{}, see the section later \bxpref{TasksPrefsAgent}.
\item Enter the \gdaut{} ID that will be given to this \gdaut{} when it is started.  
\item You can optionally create a working directory to store files in. The server directory of the installation is selected as default. To create a working directory elsewhere, browse to and select the location.  For more information on relative paths, read the section in the reference manual \bxextref{\gdrefman}{ref,relativepath}. 
\item Enter the URL of your \gdaut{}.
\bxwarn{Relative paths to the URL cannot be used!}
\item Select the browser you want to start the \gdaut{} in.
\end{enumerate}
For information on the advanced properties for the \gdaut{} configuration, see the next section \bxpref{AdvancedAUTConfigHTML}. 

\subsubsection{Advanced HTML \gdaut{} configuration}
\label{AdvancedAUTConfigHTML}

You can use the advanced dialog to enter the browser path for your browser. This lets you use a specific version of the browser (not available for Internet Explorer). 

You can also specify whether you want to be able to use the multi-window support in your tests for this \gdaut{}. If your \gdaut{} has functions that open new windows, then deactivate the \bxname{Single Window Mode} checkbox. Any \gdauts{} that are running in multi-window mode show the Selenium console as well as the \gdaut{} when the \gdaut{} is started. The \gdomeditor{} for multi-window \gdauts{} has a button to allow switching between multiple open windows for mapping components, and there are  actions in the HTML unbound modules to allow you to switch between windows during the test. 

For information on the expert properties for the HTML \gdaut{} configuration, see the next section \bxpref{ExpertAUTConfigHTML}. 

\subsubsection{Expert HTML \gdaut{} configuration}
\label{ExpertAUTConfigHTML}

You can use the expert dialog to enter an \bxname{ID attribute name} \bxpref{DFTWeb}. If you have used a specific tag to name components in your application, enter the tag in the Expert Configuration area. This information is then used instead of the \bxname{name} attribute in the object recognition. 

You can also select an activation method for your \gdaut{}. See the section on \gdaut{} activation \bxpref{TasksAUTActivation} for more details. 




