

The test for the meters tool contains three use cases. 
\begin{description}
\item [Taking a reading:]{ this use case takes a meter reading for a chosen flat. The actual steps of entering the reading and clicking \bxcaption{OK} or \bxcaption{Next} in the dialog are contained in the \gdcase{} \bxname{uc1} as they are reused elsewhere in the test.}
\item [Moving a tenant in:]{ this use case selects an empty flat from the hierarchy and selects the option to move a tenant into the flat. It reuses use case 1 because a reading needs to be taken for each of the three meters.}
\item [Moving a tenant out:]{ this use case selects a flat and selects the option to move a tenant out. It reuses use case 1 again to enter the readings. } 
\end{description}

In the \bxname{bound\_modules\_samples} \gdproject{}, you can see the building blocks that these use cases are made up of in the \bxname{AUT bound modules} category. 

\subsubsection{Excel files}
The meters tests use Excel files to provide most of the data they need. In the Excel files, you can see that the test can run in German and English. Change the working language before starting the \gdaut{} to start the \gdaut{} and run the test in a different language. 


\subsubsection{Concatenated parameters}
The meters application has a fairly complex tree structure in terms of the data in it. Look in the \gdcase{} \bxname{mtr\_tre\_selectNode} in the \bxname{bound\_modules\_samples} \gdproject{} to see how the treepath has been concatenated out of the concrete value \bxname{Building} and then two further parameters for the location of the meter and the meter number. This makes entering the test data easier. 
