% $Id: Filters.tex 2332 2006-06-26 08:47:50Z alexandra $
% Local Variables:
% ispell-check-comments: nil
% Local IspellDict: american
% End:
% --------------------------------------------------------
% User documentation
% copyright by BREDEX GmbH 2005
% --------------------------------------------------------
% this command can be inserted multiple times
%\gdhelpid{}
% 
%\begin{gddescription}
%\end{gddescription}
%
%\begin{gdlist}
% use the \item command for single steps
%\end{gdlist}
% change <PATH> to the same directory, file is located in
% change <FILE> to the same filename you are editing
%\bxinput{<PATH>/Links/<FILE>}
%
% other usefull commands are
%   \bxtipp{}        to create a hint
%   \bxwarn{}        to describe a warning

%\index{View!Problem!Filters}
\index{Problem View!Sorting}
\begin{itemize}
\item In the upper right-hand corner of the \gdprobview{} there are three buttons.
\begin{itemize}
\item The button on the right maximizes the view.
\item The middle button minimizes the view.
\item The button on the left is a menu.
\end{itemize}
\item From the menu button, you can choose to sort the \gdprobview{} according to the severity, description and location of the messages (i.e. by the three columns in the view).
\begin{description}
\item[Severity]{The order of severity starting at the most severe  is: error -- warning --information.}
\item [Description]{The description is alphabetically ordered.}
\item [Location]{The location is alphabetically ordered.}
\end{description}
 \item For example:
 \begin{itemize}
 \item You choose description (ascending)-- severity (descending) -- location (ascending) as the  properties to sort by.
 \item The messages will be first be alphabetically ordered (because \bxname{description} is the first sort property).
 \item Within this order, they will be ordered according to severity (i.e. if two messages are the same, the most severe will be first).
 \item Then they will be ordered according to location. If the description and severity are the same for two messages, they will be ordered according to location name. 
 \end{itemize}
\end{itemize}
