% BREDEX LaTeX Template
%  \documentclass is either ``bxreport'' or ``bxarticle''
%                 option is bxpaper
%% \documentclass{bxarticle}
%% % ----------------------------------------------------------------------
%% \begin{document}
%% \title{}
%% \author{}
%% % \author*{Hauptautor}{Liste der Nebenautoren}
%% \maketitle
%% % ----------------------------------------------------------------------
%% \bxversion{0.1}
%% %\bxdocinfo{STATUS}{freigegeben durch}{freigegeben am}{Verteilerliste}
%% \bxdocinfo{DRAFT}{}{}{}
%% % ----------------------------------------------------------------------

%% \end{document}
\index{Language!Working}
\index{Working language}
\label{tasksworkinglang}
\begin{itemize}
\item On the toolbar, there is a button with a globe on it. This is the \bxname{working language} button. 
\item The working language defines which  language your \gdaut{} will be started in.
\item The \gddatasetsview{} is also automatically set to accept data for the current working language.
\item The working language affects which \gdsuites{} you can edit. Only \gdsuites{} whose \gdauts{} support the current working language are editable. 
\item \gdsuites{} whose \gdauts{} do not support the working language are grayed out. 
\item Clicking directly on the button will change the working language to the default language, specified when you created the \gdproject{}.
\item To see or change the default language:
\begin{enumerate}
\item Open the \gdproject{} properties via:\\
\bxmenu{Project}{Properties}{}.
\item Select the \gdproject{} option from the left-hand side of the dialog. 
\item You can now change the default language. 
\end{enumerate}
\item If you click on the arrow next to the working language button, you will see a list of the languages you selected as \gdproject{} languages. 
\bxtipp{You can change \gdproject{} languages via:\\ \bxmenu{Project}{Properties}{}}.
\item The language marked with a tick is the current working language. 
\item The status bar also shows the current working language in the bottom right-hand corner. 
\item Click on another language to change the working language. 
\end{itemize}
