% $Id: SECTIONS.tex 10532 2010-03-16 15:57:20Z alexandra $
% Local Variables:
% ispell-check-comments: nil
% Local IspellDict: american
% End:
% --------------------------------------------------------
% User documentation
% copyright by BREDEX GmbH 2004
% --------------------------------------------------------

% This file includes all section for ,,Getting Started''
% ---------------------------------------------------
\jb{} is a tool for the automated testing of 
Graphical User Interfaces (GUI's) written with Java (Swing, SWT/RCP, GEF) and HTML. 
 
\jb{} is a keyword-driven tool. You create reusable units (keywords, or \gdcases{}) and build tests from them. You can even use our library of application- and platform-independent keywords to speed up your test creation.

\gdcases{} in \jb{} can be created before your application under test \gdaut{} is available. This means that \jb{} isn't primarily a capture-replay tool. The advantage of this is that you can start writing your tests early in each development phase, and you can run them as soon as each version of your \gdaut{} is available. This keeps your testing in synch with the development, and ensures that you get prompt feedback on the state of your application. 

In \jb{}, \gdcases{} are specified abstractly. This means that \gdcases{} are easy to reuse and adapt wherever you need them in your tests. It also improves the maintainability of your tests, because a few changes can be made from a central place. 

Another advantage of testing with \jb{} is that you do not need to program to create, maintain, execute and analyse your tests. This saves time and resources.  

Overall, testing with \jb{} can reduce the cost of your automated GUI testing, while improving the quality of your software. 

\section{How to read this manual}
\input{GettingStarted/Howto/CONTENT}
\clearpage
\section{Background}
\input{GettingStarted/Intro/CONTENT}
\clearpage


