The \gdsearchresultview{} shows any items found during a search -- either via the search dialog or the \bxcaption{Show where used} action.

From the \gdsearchresultview{}, you can:

\begin{itemize}
\item Double-click on an item to open its editor. 
\item Re-run the search using the button in the top right-hand corner of the view. 
\item Perform various actions on your search results \bxpref{TasksSearchResultActions}
\end{itemize}

\subsubsection{Using search results to make wide-reaching changes to your \gdproject{}}
\label{TasksSearchResultActions}

Once you have performed a search, you can perform specific actions on the results:
\begin{itemize}
\item You can replace all reused \gdcases{} with another \gdcase{} \bxpref{TasksSearchResultReplaceTC}.
\end{itemize}

\subsubsection{Replacing a specific \gdcase{} at places where it has been reused }
\label{TasksSearchResultReplaceTC}

If you have reused a \gdcase{} at multiple places in your \gdproject{}, and later create a new \gdcase{} that should replace it, then you can perform a mass replace via the \gdsearchresultview{}. 

\bxwarn{In order to perform a mass replace, all \gdcases{} to be changed must not be in use by anyone else using the \gdproject{} - you should ensure that this is the case before performing the replace, otherwise the replace cannot be carried out.}

\begin{enumerate}
\item Perform a search that will let you see the places where you want to replace the \gdcase{} (for this action, using \bxname{Show where used} \bxpref{TasksShowWhereUsedTestCase} on the \gdcase{} to replace will show all places of reuse in this \gdproject{}). 
\item In the \gdsearchresultview{}, select all entries, or just the \gdcase{} references you want to replace with a new \gdcase{} reference. 
\bxwarn{You will only be able to perform the replace if all selected \gdcase{} references use the same original \gdcase{}.}
\item From the context menu, select:\\
\bxmenu{Replace with another \gdcase{}}{}{}\\
\item The first page of a wizard will appear. Here, you can choose the \gdcase{} you want to use as a replacement at the places you selected.
\item Click \bxcaption{Finish} to use the newly selected \gdcase{} at the places where the searched-for \gdcase{} was used, or press \bxcaption{Next} to continue to the next page of the wizard.
\bxtipp{The \gdcase{} reference names and any comments that were used for the original \gdcase{} references, will be transferred to each new \gdcase{} reference. If the original \gdcase{} reference was commented out, the replacement \gdcase{} reference will be as well.}
\end{enumerate}
