To install the standalone:

\begin{enumerate}
\item Browse to the place where you saved the installer file and start the installer.
\item You must accept the license agreement to proceed with the installation. The license agreement is also available as a .txt and a PDF file in the installation directory.
\item If you are installing on Windows 8, you will be asked whether to install the BREDEX certificate. You only need to install this if you wish to test applications designed for the modernUI desktop (i.e. Windows Store Apps). If you do wish to test these applications, then check the checkbox before continuing. You must also then perform the installation in a place with exclusive administrator rights (e.g. Program Files). If you do not wish to test modernUI applications, then you can leave the checkbox unchecked.
\item Follow the steps in the installer to install the components you require at the places you require. The available components are:
\begin{description}
\item [The \ite{}:]{This includes the \ite{} (Integrated Test Environment, the graphical client for writing tests), and the testexec and dbtool command line tools for executing tests from the command line, and importing / exporting / deleting \gdprojects{} from the command line.}
\item [The \gdagent{}:]{This includes the server component, required for starting \gdauts{} and running tests. It also contains the autrun command line tool for starting \gdauts{} without using an \gdaut{} configuration.}
\item [The documentation:]{PDF documentation}
\item [The \dash{}:]{This lets you install and start the \dash{} on a central machine so that users throughout the network can access the test results from the web application. }
\end{description}
\end{enumerate}
