% $Id: TSstart.tex 11355 2010-06-16 14:48:31Z alexandra $
% Local Variables:
% ispell-check-comments: nil
% Local IspellDict: american
% End:
% --------------------------------------------------------
% User documentation
% copyright by BREDEX GmbH 2004
% --------------------------------------------------------

\subsubsection{Starting a \gdsuite{} or a \gdjob{}}
\index{Execution!Test!Start}
\index{Test!Start}
\index{Start!Test Execution}
\index{Test Suite!Start}
\index{Start!Test Suite}
\index{Start!Test Job}
\index{Test Job!Start}

To start a \gdsuite{} or a \gdjob{}, you must:
\begin{itemize}
\item have started the \gdaut{} \bxpref{startaut}
\item have completed object mapping for the \gdsuite{} or \gdsuites{} \bxpref{objectmappingtasks}
\item have entered complete test data for your \gdsuites{}, for the language you want the test to run in.  
\end{itemize}

\bxtipp{Before starting a \gdsuite{}  or a \gdjob{}, it is a good idea to review your preferences for the test results \bxpref{testresprefs}.}


\begin{description}
\item [Starting a \gdsuite{}:]{You can start a \gdsuite{} from the \gdtestsuitebrowser{} or from the \jb{}unautview{}. Click on the arrow next to the \bxcaption{Start test execution} button and select a \gdsuite{} to start from the list.}
\item [Starting a \gdjob{}:]{You can start a \gdjob{} from the \gdtestsuitebrowser{}. Click on the arrow next to the \bxcaption{start test execution} button and select a \gdjob{} to start from the list.}
\end{description}

\gdmarpar{../../../share/PS/startSuite}{ start test}


\bxtipp{The amount of \gdsuites{} or \gdjobs{} in the list for the \bxcaption{start test} button depends on your selection. In the \jb{}unautview{}, only \gdsuites{} for the currently selected \gdaut{} will be shown. In the \gdtestsuitebrowser{}, if you have selected a \gdsuite{} or a \gdjob{}, only the selected item will be startable. } 

\subsubsection{Stopping a \gdsuite{} or \gdjob{}}
\index{Test!Stop}
\index{Execution!Test!Stop}
\index{Stop!Test Execution}
\index{Test Suite!Stop}
\index{Stop!Test Suite}
\index{Test Job!Stop}
\index{Stop!Test Job}

To stop the test at any point, click on the  \bxcaption{stop test execution} button on the toolbar. 
 \gdmarpar{../../../share/PS/stop}{ stop test}
The test stops automatically when it finishes or when an error occurs whose \gdehandler{} has \bxname{exit} as a reentry type. 

\subsubsection{Pausing a \gdsuite{} or \gdjob{}}
\label{PauseExec}
\index{Pause Test Execution}
\index{Execution!Test!Pause}
\index{Test!Pause}
\index{Test Suite!Pause}
\index{Pause!Test Suite}
\index{Test Job!Pause}
\index{Pause!Test Job}

\begin{enumerate}
\item To pause a test, click on the \bxcaption{pause test execution} button on the main toolbar. 

 \gdmarpar{../../../share/PS/pause}{ pause test}
 \item To continue with the test, press the \bxcaption{Pause test execution} button again.
 \bxwarn{If the client and \gdagent are installed on the same machine, moving the mouse will disrupt the test. } 
 \end{enumerate}
