Descriptions are longer pieces of text that provide information about nodes in your tests. You can add descriptions in the \ite{} to \gdcases{}, \gdsuites{} and \gdjobs{} via the editor for these items. You can add descriptions to the item itself, or to other items used in it. 


\begin{enumerate}
\item Open the editor containing the item you want to add a description to. 
\item Select the item you want to add, and select from the context-sensitive menu:\\
\bxmenu{Edit Description}{}{}
\item In the dialog that opens, you can enter text in the upper field. The text you enter can use the syntax of various markup languages (e.g. TracWiki, MediaWiki). You can set the language for your \gdproject{} in the \gdproject{} properties \bxpref{ProjPropertiesGeneral}. \\
In the lower field, you can see the preview of the text as it will appear in the description view. The preview is updated after a short pause in typing.
\item Click \bxcaption{OK} to close the dialog. You will see the description you have entered in the description view. If the description view is not open, you can open it by selecting:\\
\bxmenu{Window}{Show View}{Description}
\item The changes to your descriptions are saved when you save the editor.
\item You can add a description for the original specification of a \gdcase{} or a \gdsuite{}, and also at places where a \gdcase{} or \gdsuite{} has been reused. You can add a new description to overwrite an existing one when you reuse an item. 
\item Descriptions are not displayed in test results.
\end{enumerate}
