% BREDEX LaTeX Template
%  \documentclass is either ``bxreport'' or ``bxarticle''
%                 option is bxpaper
%% \documentclass{bxarticle}
%% % ----------------------------------------------------------------------
%% \begin{document}
%% \title{}
%% \author{}
%% % \author*{Hauptautor}{Liste der Nebenautoren}
%% \maketitle
%% % ----------------------------------------------------------------------
%% \bxversion{0.1}
%% %\bxdocinfo{STATUS}{freigegeben durch}{freigegeben am}{Verteilerliste}
%% \bxdocinfo{DRAFT}{}{}{}
%% % ----------------------------------------------------------------------

%% \end{document}

\index{Test Suite!Failed}
If your test fails, you can find exact details about the problem by looking at the \gdtestresultview{} \bxpref{testresultview}.

For other problems with test execution, check:

\begin{itemize}
\item That the \gdaut{} is in focus and is visible. You can automatically activate the \gdaut{} in the \gdaut{} properties \bxpref{configuringaut}. You can also set your preferences to minimize \app{} when test execution begins \bxpref{gdprefs}. 
\item That the \gdaut{} is ready when the test begins. To ensure this, you can insert a \gdcase{} at the beginning of each test which waits for the window or for the first component you want to test. 

\bxtipp{Waiting for a window to appear is generally a good idea whenever a new window or dialog is opened during the test. Waiting for the window or the component you want to test will make sure that your tests run even under different timing conditions.  }
\item Make sure that the \gdcases{} and \gdsteps{} are in the right order.
\item Ensure that the data you have entered is correct.
\item Check your object mapping preferences \bxpref{objectprefs}. We recommend that you set them to \bxcaption{standard}.
\item If the \gdaut{} is an RCP application, make sure that the keyboard layout is correct \bxpref{configuringaut}. Otherwise, make sure you have the current version of the RCP-Accessor (start your application with -clean to be sure).  
\item Check that the \gdsteps{} preceding the failed \gdstep{} were successful by looking at the state of the application.  
\end{itemize}
