% $Id: intro.tex 12304 2010-09-23 14:35:36Z alexandra $
% Local Variables:
% ispell-check-comments: nil
% Local IspellDict: american
% End:
% --------------------------------------------------------
% User documentation
% copyright by BREDEX GmbH 2005
% --------------------------------------------------------
% this command can be inserted multiple times
%\gdhelpid{}
% 
%\begin{gddescription}
%\end{gddescription}
%
%\begin{gdlist}
% use the \item command for single steps
%\end{gdlist}
%% change <PATH> to the same directory, file is located in
% change <FILE> to the same filename you are editing
%\bxinput{<PATH>/Links/<FILE>}
%
% other usefull commands are
%   \bxtipp{}        to create a hint
%   \bxwarn{}        to describe a warning
\index{Troubleshooting}
\label{errorHandling}

\subsection{General help}
Always check in the \gdprobview{} first for any help with your tests. The messages there should help you with most of the problems. The \ite{} also highlights problems in the browsers and views with red crosses. Hover the mouse over the item to see a tool tip with more information. 

In some text fields you can only enter certain characters. A red background in a text field means that you have entered something incorrect in that field. A yellow background means that the information entered is incomplete. 

Looking in the log files may help to resolve some problems. Logs for the client (\ite{}) and \gdagent{} can be found via:\\
\bxmenu{Help}{Show Client/\gdagent Log}{}
\bxtipp{The \ite{} can only access an \gdagent{} log file if it is currently connected to a \gdagent{}.}

This section contains information on some of the more common problems:
\begin{itemize}
\item Starting the \gdagent{} \bxpref{troublestartserver}.
\item Connecting to the \gdagent{} \bxpref{troubleconnectserver}.
\item Starting the \gdaut{} \bxpref{troublestartaut}.
\item Mapping components from the \gdaut{} \bxpref{troubleobjectmapping}.
\item Executing \gdsuites{} \bxpref{troubleexecute}.
\item Failed \gdsuites{} \bxpref{troublefailed}. 
\item Locked \gdcases{}   \bxpref{troublelocked}.
\end{itemize}


For other problems, look in the relevant section of the user manual or the reference manual. There are also FAQs on the BREDEX website.



