\index{Support Email}


You can send support emails to \jb{} support from within the \jb{} client. The advantage of doing this is that you have the option to automatically attach information to the mail, which will help our support team to help you. 

\begin{enumerate}
\item Select:\\
\bxmenu{Help}{Support Request Email}{}
\item In the dialog which appears, select what to add to the email: 
%pic
\bxtipp{The more information you add, the more likely we are to be able to fix the problem quickly!}
\begin{description}
\item [Configuration information:]{This includes information about how you have configured \jb{}, which other plugins you are using, and information about your environment that is useful to the \jb{} support team when dealing with your queries. }
\item [The \gdserver{} log]{This lets us see the messages from the \gdserver{}. If you are not connected to the \gdserver{}, this option will be grayed out. }
\item [The client log]{This lets us see the messages from the client. }
\item [The \gdproject{} and depending \gdprojects{}]{Sending us your \gdproject{} and the \gdprojects{} it reuses will help us to identify any problems in your specification or \gdaut{} configuration. }
\end{description}
\bxtipp{Any \gdprojects{} you add are first exported to a temporary directory on your computer.}
\item Click \bxcaption{OK}. 
\item The prepared email will be opened with the selected attachments already added. 
\item Enter a text with a short description of the problem, and send us the email. 
\item We will be in touch with an answer as soon as possible. 
\end{enumerate}
