This situation occurs when a component name that has been propagated and then renamed at the place of reuse is no longer accessible, either because:

\begin{itemize}
\item the name with which the component was propagated has been changed, or
\item the checkbox to propagate the component name has been deactivated.
\end{itemize}
In such situations, you will see the message in the \gdcompnamesview{} :\\
\bxname{No Component Type Exists!}.

\bxtipp{Saving the \gdcase{} will remove the message, however, you may want to take steps to transfer the component name before removing the message.}

\begin{itemize}
\item An example of a situation where this occurs:
\begin{enumerate}
\item You have a \gdcase{} \bxname{TC1} that has a component name propagated from it:  \bxname{nn\_nn\_grc}.
\item You reused the \bxname{TC1} \gdcase{} in another \gdcase{} called \bxname{TC2}, and renamed the component name to \bxname{LoginDialog\_OK\_btn} at the place of reuse.
\item You then either:\\
\begin{itemize}
\item change the component name in the original \gdcase{} to \bxcaption{LoginDialog\_AnyButton\_btn}, 
\item or you deactivate the checkbox for propagating the component name from the original \gdcase{}.
\end{itemize}
\end{enumerate}
\item In the \gdcompnamesview{} for the reused \gdcase{} in \bxname{TC2}, you will see a warning message that the component name has no type. 
\bxwarn{The warning field is not editable.}
\item Depending on whehter you renamed the component name or removed the checkbox, you can now do one of two things:
\begin{itemize}
\item If you renamed the component name in the original \gdcase{} (\bxname{TC1}, then you can locate the newly propagated name in the \gdcompnamesview{} and enter the \bxname{new name} for the no longer existent component type in the \bxname{new name} field for the newly propagated name. This essentially points the previous component name hierarchy onto the new one.
\item If you deactivated the checkbox, or if you do not want to transfer the name as mentioned above, you can simply make any change to the \gdcase{} and then save it. The message will disappear.
\end{itemize}
\end{itemize}
