\chapter{Introduction}
\label{introduction}

\gdauts{} are started, controlled and observed using its remote control component. In
order for the \gdagent to know how to control each element of a GUI, we have
outfitted the \gdagent with a pluggable interface for graphic components. An
adapter factory containing one or more components must be implemented for and
deployed with the \gdaut. On the client side, each GUI toolkit that the \ite{}
supports is described in a toolkit plug-in.

We have opened up an interface to our users to allow flexible
customizations. You can extend existing functionality, or provide support for
in-house graphic components by implementing your own \textbf{\gdtesterclasses.}

This handbook shows general steps for creating \ite{} toolkit extensions, which
is described in chapter \ref{toolkitExtension}. In this chapter you will find
also  a short description of the extension examples. Last but not least chapter
\ref{functions} describes how to create a custom \ite{} function, which can be
used in tests.

\chapter{Creating toolkit extensions}
\label{toolkitExtension}

The following chapter describes the general steps to take for creating an \ite{}
toolkit extension with custom defined components and actions. This chapter
begins by listing the requirements followed by showing the necessary steps
for creating an \ite{} and remote control extension. The \ite{} toolkit extension is
described in section \ref{iteExtension} and the implementation for the remote
control extension in section \ref{remoteControlExtension}.

Extension examples with source code can be found in the subdirectory\\
\bxshell{examples/development/extension/src/}\\
of the  installation.

In general you always have to extend two things:
\begin{itemize}
\item The \ite{} toolkit extension --  by writing your own \textbf{toolkit} plug-in:\\
      This will tell the \ite{} which new components and actions are
      available.
\item The remote control extension -- by writing your own \textbf{fragment}:\\
      This part actually performs the actions on the new components.
\end{itemize}

In this chapter all used directory names are located in the
installation directory  as long as nothing else is specified.

\section{Requirements}
To create your own \ite{} toolkit and remote control extensions, you need:
\begin{itemize}
\item \textbf{GUI}\emph{dancer} 7.0 / Jubula 2.0 or later
\item Eclipse 3.4 or later (4.2 recommended)
\item JDK 5.0
\item Full write access in installation directory for deploying the
extension.
\end{itemize}

\section{\ite{} extension}
\label{iteExtension}

This section shows you how to develop the \ite{} toolkit extension. We describe the
steps to create the toolkit plug-in and how it can be exported.

\subsection{Creating the toolkit plug-in}

The following steps have to be done to extend the \ite{} toolkit:
\begin{enumerate}
 \item Create a \textbf{Plug-in Project} for your toolkit project.
 \item Create a \textbf{Feature Project} referencing your toolkit project from
 the previous step for an easier installation into the \ite{}.
 \item Set the features
       \begin{itemize}
        \item \bxname{org.eclipse.rcp} and
        \item \bxname{org.eclipse.jubula.feature}
       \end{itemize}
       from the installation folder as
       your \textbf{Target Platform} in the workspace preferences. Information
       on configuring the target platform can be found in Eclipse's online Help
       under \bxname{Plug-in Development Environment Guide > Tools >
       Preferences > Target Plug-ins}.
 \item Add the following dependencies to your toolkit project:
       \begin{itemize}
        \item \bxname{org.eclipse.jubula.tools} and
        \item \bxname{org.eclipse.jubula.toolkit.common}
       \end{itemize}
 \item Use and configure the following extension point in your toolkit
       project:\\
       \bxname{org.eclipse.jubula.toolkit.common.toolkitsupport}.
 \item Implement the interface \bxshell{IToolkitProvider} from the extension
 point of the previous step.
 \item Create the definition of your own toolkit in the file\\
       \bxshell{ComponentExtension.xml} by choosing one or more of the following
       possibilities:
       \begin{itemize}
        \item Extend existing toolkit components with new actions,
        \item derive new components from existing toolkit components, or
        \item define a new toolkit component.
       \end{itemize}
 \item Manage the i18n keys in the properties file.
\end{enumerate}

You will find projects in zip-files as a showcase for steps 1-8, which are
located in the directory\\
\bxshell{examples/development/extension/src}.\\
Each zip-file contains an example for a specific toolkit, e.g. a Swing example
extends the \bxshell{JSlider} component.

These example projects can be simply imported into your Eclipse workspace. Set
the target after importing the projects as described in step 3. All other steps
have already been done in the examples.

\subsection{Deploying the toolkit plug-in}

Once the toolkit feature has been created, it must be deployed in the \ite{}.
The toolkit feature must be exported to an update site and then installed via
this update site into  the \ite{}.
If you want to execute tests on your new components via testexec, it is important
that you have write access to the \ite{} so that the installed feature can be 
accessed during test execution. 
 
\subsubsection{Create an update site for the toolkit feature}

\begin{enumerate}
\item Create an \textbf{Update Site Project}.
\item Add a category to your update site that defines its \bxname{ID} and
      \bxname{Name}.
\item Add your toolkit feature to the category created in the previous step.
\item Build the created toolkit update site. The directory of the toolkit
      update site project serves as an update site, which is later used to
      install your toolkit feature into the \ite{}. Remember to build and then
      synchronize this update site if you have changed the toolkit feature.
\end{enumerate}

\subsubsection{Install the toolkit feature from the update site}

\begin{enumerate}
\item Start the \ite{}  and select from the main menu\\
\bxmenu{Help}{Install new software...}{}.
\item Click the \bxcaption{Add...}
button in the \bxname{Install} dialog that appears.
\item Click the \bxcaption{Local...} button in the \bxname{Add Repository} dialog
that appears
\item Navigate to the directory that contains your update site and confirm your
selection.
\item Click \bxcaption{OK} to exit the \bxname{Add Repository} dialog.
 The active dialog should now be \bxname{Install}.
\item Ensure that the check box named \bxname{Group items by category} is
deselected. Your feature should be visible in the central table of the dialog.
\item Ensure that the check box next to your feature is selected and click
 \bxcaption{Next}.
\item Confirm the \bxname{Installation Details} by clicking the \bxcaption{Next}
 button again.
\item Accept the license agreement terms and click \bxcaption{Finish}.
\item A warning dialog may appear to warn you are installing unsigned content.
 Click \bxcaption{OK} in this dialog if the feature comes from a trusted
 source. This should be the case as long as you install your own feature.
 Then the installation process begins.
\item Click the \bxcaption{Restart Now} button to perform a restart,
 when a dialog appears to prompt the restart that will safely
 finish the update / installation.  After the restart your \ite{} toolkit extension
 feature is installed.
\end{enumerate}

\section{Remote control extension}
\label{remoteControlExtension}

\gdauts{} are controlled by the remote control called \gdagent. The \ite{}
can also execute the remote control if the embedded \gdagent{}  is
used. Otherwise, the normal \gdagent{} runs as a remote control in a
separate process independently from the \ite{}.
For each supported component known, a \gdtesterclass must exist.
This class implements the test actions that can be carried out on the component.
You need to write a fragment for your component, which contains the
\gdtesterclass and a corresponding adapter factory.

\subsection{Creating the fragment}

The following steps have to be done to extend the remote control:

\begin{enumerate}
  \item Reference the zip-file\\
        \bxshell{development/extension-toolkit-rc.zip}\\
        as a \textbf{Software Site} in your \textbf{Target Platform}.
        Verify while adding the software site, that the check box
        \textbf{Include required software} is not checked. This software site also
        includes the Java documention of the source code.\\
	If you are writing an extension for the JavaFX toolkit, you need to clone
	the Jubula repository to get access to the required source code because it
	is not yet available in the zip-file.
  \item Set the installed software site as your target platform.
  \item Create a fragment project with one of the following IDs as host:
    \begin{itemize}
      \item \bxshell{org.eclipse.jubula.rc.swing}\\
            for extending Swing support.
      \item \bxshell{org.eclipse.jubula.rc.swt}\\
            for extending SWT support without RCP environment.
      \item \bxshell{org.eclipse.jubula.rc.rcp.swt}\\
            for extending SWT support in Eclipse 3.x and 4.x (including compat
            layer).
      \item \bxshell{org.eclipse.jubula.rc.rcp.e3.swt}\\
            for extending GEF support in Eclipse 3.x (without compat
            layer).
      \item \bxshell{org.eclipse.jubula.rc.javafx}\\
            for extending JavaFX support.
   \end{itemize}
  \item Write your own adapter and \gdtesterclasses.
\end{enumerate}

\bxtipp{If you are writing an extension for the JavaFX toolkit, make sure that your
adapter and \gdtesterclasses really get compiled with Java 8.}

Adapters are used for all supported toolkits, i.e. Swing, SWT, GEF, RCP and JavaFX.
They wrap and specify graphic components in a form we need for our
\gdtesterclasses. You can write your own adapter or reuse our existing
adapters. We recommend reusing our adapters to take advantage of the already
existing code.

Before we have a look at the remote control extension examples in section
\ref{extensionExamples}, we describe in general how to create an
adapter and \gdtesterclasses.

\subsubsection{Creating an adapter}

To use an adapter you have to implement the interface\\
\bxshell{IAdapterFactory}, which is defined in the package named\\
\bxname{org.eclipse.jubula.rc.common.adaptable}.\\
It is necessary that the implementation of this interface resists in a package
named\\
\bxname{org.eclipse.jubula.rc.common.adapter}.\\
The package naming is important for the remote control extension, because
adapters can only be found if they are located in a package with the mentioned name.

In order to support your own components, the targeted type must be an instance
of \bxshell{IComponent}, which is defined in the package named\\
\bxname{org.eclipse.jubula.rc.common.tester.adapter.interfaces}.\\
This targeted type can be used for text components. If you want to support your
own graphical component, you should at least use the interface
\bxshell{IWidgetComponent} as the targeted type, which is a child of
\bxshell{IComponent}. Both interfaces are defined in the same package.

For Swing, SWT and JavaFX there are also specific implementations of different
adapters in the following packages, which can be used for your own component:\\
\bxname{org.eclipse.jubula.rc.swing.tester.adapter}\\
\bxname{org.eclipse.jubula.rc.swt.tester.adapter}\\
\bxname{org.eclipse.jubula.rc.javafx.tester.adapter}

Now we know how to create an own adapter in general. The next step is to
implement one or more \gdtesterclass. 

\subsubsection{Creating a \gdtesterclass}

The functionally important aspect of a \gdtesterclass is that it
contains public methods for the test actions, which will appear in
the client. These methods are linked to testable actions within a user-defined
\ite{} toolkit plug-in.

Each \ite{}  toolkit extension provides an XML configuration file, which defines the
available methods with parameters, as well as information for string
externalization. Reflection is used to call these methods. For this reason, the
signature of a defined method including its name, and the ordered parameter
types are important for the remote control extension.

You can write your own \gdtesterclasses, but if you only want to support a new
component with existing actions, you could use one of our existing
\gdtesterclasses, which you can find in the package named\\
\bxname{org.eclipse.jubula.rc.common.tester}. For Swing, SWT and JavaFX there are also
specific implementations in the following packages:\\
\bxname{org.eclipse.jubula.rc.swing.tester}\\
\bxname{org.eclipse.jubula.rc.swt.tester}\\
\bxname{org.eclipse.jubula.rc.javafx.tester}

Please take the following guidelines into consideration for creating
\gdtesterclasses:
\begin{itemize}
  \item The class must be compatible with \bxname{Java 1.4}.
  \item It must either implement
  \begin{itemize}
    \item the interface \bxshell{ITester} defined in the package named\\
        \bxname{org.eclipse.jubula.rc.common.tester.interfaces},\\
	 \item or the abstract class \bxshell{AbstractUITester}
	     defined in the package named\\
	     \bxname{org.eclipse.jubula.rc.common.tester}.
  \end{itemize}
  \item The component must provide \textbf{public} methods for all actions
        declared by the XML configuration file of the corresponding \ite{}
        toolkit extension.
  \item Each method that implements an action must throw a\\
        \bxshell{StepExecutionException}\\
        defined in the package named\\
        \bxname{org.eclipse.jubula.rc.common.exception}
        to notify the \ite{} if the execution of the action has  failed.
\end{itemize}

\subsection{Deploying the fragment}

Once you have written your fragment, you still need to make all components
aware of its presence. This is done by exporting the fragment and
deploying it into the remote control.

There are different ways for installing your fragment into the remote
control, depending on the  \gdagent{} used and the specific \gdaut{}. You are free to
use either the embedded \gdagent{} or the standalone \gdagent{}. Also your \gdaut{}
can be based upon the OSGi framework or not. The following table shows an
overview, where to deploy your fragment:

\begin{center}
\begin{tabular}{|c||c|c|}
\hline
~ & without OSGi & with OSGi\\
~ & (Swing, SWT, JavaFX) & (RCP, GEF)\\
\hline\hline
embedded & \multirow{2}{*}{\ite{}} & \multirow{4}{*}{AUT}\\
AUT agent & & \\
\hhline{--~}
standalone & standalone & \\
AUT agent  & AUT agent  & \\
\hline
\end{tabular}
\end{center}

It shows, in which case you usually deploy your fragment into
\begin{itemize}
  \item the \ite{} with a feature including your fragment,
  \item the standalone \gdagent{} by adding your fragment to its configuration,
        or
  \item the \gdaut{} with a feature including your fragment.
\end{itemize}

The configuration of the standalone \gdagent{} can be done by modifying the
file\\
\bxshell{server/configuration/config.ini}\\
There you have to append \bxshell{,fragment\_id} at the end of the line starting
with \bxshell{osgi.bundles=}. Make sure that the bundles are comma-separated.
It is also necessary to add the argument \bxshell{-clean} in the file
\bxshell{server/autagent.ini}, when deploying a new version with the same
fragment ID. Apart from the deploying methods mentioned, it is also possible to
install your fragment using a p2 repository or the OSGi console.

You should be able to test your new component once you have installed the
toolkit feature into the \ite{} and the fragment as described below.

\section{\ite{} and remote control extension examples}
\label{extensionExamples}

In the installation, there are source code examples for extending supported toolkits. The
examples can be found in the directory\\
\bxshell{examples/development/extension},\\
which contains the following sub-folders:

\begin{description}
 \item[src] Contains some zip-files with example source code projects, which
            can be imported by Eclipse:
 \begin{itemize}
   \item \bxshell{RCPExtension.zip}\\
         An extension supporting \bxshell{Group} for SWT including client
         and remote control projects. After deploying these projects you should
         be able to test the \bxshell{Group} in RCP applications.
   \item \bxshell{SwingAUT.zip}\\
         An AUT using \bxshell{JSlider} from Swing.
   \item \bxshell{SwingExtension.zip}\\
         The  extension supporting \bxshell{JSlider} for Swing including
         client and remote control projects. After deploying these projects you
         should be able to test the \bxshell{JSlider} in the Swing example AUT.
   \item \bxshell{SwingRendererExtension.zip}\\
         A remote control extension supporting a custom graphics
         component for Swing.
 \end{itemize}
 \item[AUT]  Contains the binary file \bxshell{JSlider.jar}, which is a simple
 example AUT using the normally unsupported component \bxshell{JSlider}. After
 installing the \bxshell{JSlider} example extension from the \textbf{src}
 folder, you will be able to test this new component.
\end{description}
