\index{Test Job!Add Test Suite}
\label{AddSuiteToJob}

To add \gdsuites{} to a \gdjob{}, you must first create one \bxpref{createtestjob}.

\begin{enumerate}
\item Open the \gdjobeditor{} by double-clicking on the \gdjob{} you want to edit.


\item Add \gdsuites{} to a \gdjob{} in the \gdjobeditor{} using drag-and-drop from the \gdtestsuitebrowser{}.


  \item The \gdsuite{} or \gdsuites{} you added appear(s) in the \gdjobeditor{}. They are marked with a small arrow to show that they are reused here. The name of the \gdjob{} is contained in angled brackets (\bxshell{< >}) to show that it is the same name that you used when you specified the \gdsuite{}. 

\item Once you have added a \gdsuite{}, you must select the \gdaut{} ID that you wish to run this \gdsuite{} on from in the \gdpropview{}. This enables you to differentiate between multiple \gdauts{} (or instances of the same \gdaut{} in your tests). 
\bxtipp{You must have defined all \gdauts{} to be tested during a \gdjob{} in the \gdaut{} definition dialog \bxpref{Defineaut}.}
\item Save the changes in the editor.

\end{enumerate}

\subsubsection{Deleting \gdsuites{} from a \gdjob{}}
\index{Delete!Test Suites}
\index{Test Suite!Delete}
\label{TasksDeleteSuiteJob}

\begin{enumerate}
\item Open the \gdjobeditor{} by double-clicking on the \gdjob{} you want to edit.
\item  Single-click the \gdsuite{} you want to delete. Use  \bxkey{Ctrl} to select multiple \gdsuites{}. 
\item Select \bxcaption{delete} from the context-sensitive menu to delete the \gdsuites{}.
\item \gdsuites{} can also be deleted using \bxkey{DELETE}.
\item Confirm that you want to delete the \gdsuites{} in the dialog which appears.
\item Save the changes in the \gdjobeditor{}. 

\end{enumerate}

\subsubsection{Renaming \gdjob{}}
\gdhelpid{dialogRenameContextId}{Rename Dialog}
\index{Rename!Test Job}
\index{Test Job!Renaming}
\label{TasksRenameJob}
\begin{enumerate}
\item \gdjobs{} can be renamed in one of two ways:
\begin{enumerate}
\item Select the \gdjob{} you want to rename in the \gdtestsuitebrowser{}. Select:\\
\bxmenu{Rename}{}{}\\
from the context-sensitive menu. In the dialog which appears, enter a new name and click \bxcaption{OK}. 
\item Open the \gdjobeditor{} by double-clicking on the \gdjob{} you want to edit in the \gdtestsuitebrowser{}.  In the \gdpropview{}, change the \gdjob{} name. Save the changes in the editor.  
\end{enumerate}
\end{enumerate}
