\begin{enumerate}
\item You can delete items from the \gdomeditor using the \bxcaption{delete} option from the context-sensitive menu.
\item You can also select the item you want to delete and press \bxkey{DELETE}.
\item If you delete a component name that is still used in a \gdcase{} for this \gdsuite{}  it will reappear  when you select \bxcaption{refresh} from the context-sensitive menu.
\end{enumerate}

\bxtipp{If you want to remove all unused mappings from the \gdomeditor{}, then use the \bxname{Cleanup} option \bxpref{TasksOMCleanup}.}

\subsubsection{Removing unused component names from the \gdomeditor{}}
\gdhelpid{objectMapEditorContextId}{Object Mapping}
\label{TasksOMCleanup}
\index{Cleanup!Object Mapping Editor}
\index{Object Mapping!Editor!Cleanup}

Over time, your \gdproject{} will change, and these changes may mean that component names you had previously used in \gdsuites{}, then mapped to technical names via the Object Mapping, are no longer used. This results in object mappings in which the component name is no longer used in the test for this \gdaut{}. Such component names can be recognized by the fact that \bxname{Show corresponding specification} in the \gdomeditor{} \bxpref{TasksSearchCompNameCorresponding} returns no search results in the search result view (i.e. the component name is no longer used in the test), or if the search result view shows only \gdcases{} that are used in other \gdauts{}. If you perform \bxname{Show where used} in the \gdcompnamebrowser{} \bxpref{TasksSearchCompNameBrowserShowWhereUsed} and the only search result is a mapping, then this is also a component name that is no longer used in the test. 

You can delete any component names from the \gdomeditor{} that are unused in the \gdproject{} for this \gdaut{}:

\begin{enumerate}
\item In the \gdomeditor{}, select:\\
\bxmenu{Cleanup}{unused component names}{}\\
from the context-sensitive menu. 
\item The cleanup operation starts, and a progress dialog is shown while unused names are being searched for. Depending on the size of your \gdproject{}, this search may take some time. 
\item If the \gdomeditor{} contains component names that are not used in any of the \gdsuites{} for this \gdaut{} (either component names that are already mapped, or are still unassigned), then they are shown in a \bxname{Delete unused component names} dialog. 
\bxtipp{If no component names are found, then you will see a message informing you of this.}
\item In the dialog to delete unused component names, you can see which component names have been identified for deletion. You can deselect individual component names to opt not to delete them. Once you have specified which component names should be deleted, click \bxcaption{OK}. 
\item The component names you specify will be deleted from the \gdomeditor{}. Save the editor to save the changes. 
\bxwarn{Removing component names from the \gdomeditor{} does not mean that the component names are deleted from the \gdproject{}. However, if the deletion from the object map means that the component name is now used nowhere in the \gdproject{}, then it will appear under the \bxname{Unused Component Names} category in the \gdcompnamebrowser{} and can be deleted from the whole \gdproject{} \bxpref{TasksDeleteCompName}}.
\end{enumerate}
