\index{Test Case!Edit}
\index{Edit!Test Case}

\begin{enumerate}
\item To edit a \gdcase{}, double-click on the \gdcase{} you want to edit in the \gdtestcasebrowser{}. 
\item The \gdtestcaseeditor{} for this \gdcase{} will appear in the middle of the specification perspective. 

\bxtipp{When you are working in the \gdtestcaseeditor{}, the \gdpropview{}, \gddatasetsview{} and \gdcompnamesview{} on the right hand side of the screen contain information about this \gdcase{}.} 
\item From the \gdtestcaseeditor{}, you can edit this \gdcase{}. You can:

\begin{itemize}
\item add other \gdcases{} \bxpref{addtestcase}.
\item add and edit \gdsteps{} \bxpref{specsteps}.
\item rename the \gdcase{} \bxpref{renamingtc}.
\item add a comment to the \gdcase{} \bxpref{taskscomment}.
\item add, edit or translate data for the \gdcase{} \bxpref{TasksDataSetsView}. 
\end{itemize}
\end{enumerate}

\subsection{Renaming \gdcases}
\index{Test Case!Renaming}
\index{Renaming!Test Cases}
\label{renamingtc}
\subsubsection{Renaming \gdcases{} from the \gdtestcasebrowser{}}
\gdhelpid{dialogRenameContextId}{Renaming}
\begin{enumerate}
\item There are two ways to rename a \gdcase{} from the \gdtestcasebrowser{}:
\begin{enumerate}
\item Select the (non-reused) \gdcase{} you want to rename in the \gdtestcasebrowser{}. Select:\\
\bxmenu{Rename}{}{}\\
from the context-sensitive menu. In the dialog which appears, enter a new name and click \bxcaption{OK}. 
\item Open the \gdtestcaseeditor{} by double-clicking on the \gdcase{} you want to edit in the \gdtestcasebrowser{}.  In the \gdpropview{}, change the \gdcase{} name. Save the changes in the editor. 
\end{enumerate}

Renaming a \gdcase{} in the \gdtestcasebrowser{} or in its \gdtestcaseeditor{} changes the \bxname{specification name} of the \gdcase{}. 

If you have reused this \gdcase{} in other \gdcases{} or \gdsuites{}, the name will also be changed in the places where you have reused it but not renamed it. 


\end{enumerate}

\subsubsection{Renaming a \gdcase{} reused in another \gdcase{}}
\gdhelpid{dialogRenameContextId}{Renaming}
\begin{enumerate}
\item Open the \gdtestcaseeditor{} by double-clicking on the \gdcase{} you want to edit in the \gdtestcasebrowser{}. 
\item In the \gdtestcaseeditor{}, select the \gdcase{} you want to rename.
\item In the \gdpropview{}, enter the new name for the \gdcase{} in the \bxname{Test Case name} field. 

The angled brackets from the \gdcase{} you just edited will disappear from the \gdtestcaseeditor{}. This indicates that the \gdcase{} has been renamed. You will still see the original \gdcase{} name behind the new name in brackets. In the preferences, you can opt not to see the original name when you have renamed a \gdcase{} reference \bxpref{gdprefs}. 

The original \gdcase{} in the \gdtestcasebrowser{} still has its original name. The reused \gdcase{} you just renamed will keep its new name even if you rename the original \gdcase{}. 

If you want to reset the original specification name in a reused \gdcase{}, empty the \bxname{Test Case name} field and save the editor. The \gdcase{} will redisplay the angled brackets and will have the same name as the specification name.  
\end{enumerate}

\subsubsection{Renaming a reused \gdcase{} in a \gdsuite{}}
\gdhelpid{testSuiteEditorContextId}{Test Suite Editor}
%\gdhelpid{testExecViewContextId}{Test Suite Browser}
\begin{enumerate}
\item Open the \gdtestsuiteeditor{} by double-clicking on the \gdsuite{} you want to edit in the \gdtestsuitebrowser{}. 
\item In the \gdtestsuiteeditor{}, select the \gdcase{} you want to rename.
\item In the \gdpropview{}, enter the new name for the \gdcase{} in the \bxname{Test Case name} field. 

You will still be able to see the original \gdcase{} name (the specification name) in the \gdpropview{}. The angled brackets from the \gdcase{} you just edited will disappear from the \gdtestsuiteeditor{}. This indicates that the \gdcase{} has been renamed. 

The original \gdcase{} in the \gdtestcasebrowser{} still has its original name. The reused \gdcase{} you just renamed will keep its new name even if you rename the original \gdcase{}. 

If you want to reset the original specification name in a reused \gdcase{}, empty the \bxname{Test Case name} field and save the editor. The \gdcase{} will redisplay the angled brackets and will have the same name as the specification name.  
\end{enumerate}


\subsection{Adding comments to \gdcases{} and \gdsuites{}}
\index{Add!Comments}
\index{Comment!Add}
\label{taskscomment}
\begin{enumerate}
\item Open the \gdtestcaseeditor{} or \gdsuiteeditor{} by double-clicking on the  \gdcase{} or \gdsuite{} you want to add a comment to.
\item This will open the editor for the \gdcase{} or \gdsuite{}. 
\item Enter a comment in the \bxname{comment} field in the  \gdpropview{}. 
\item Save the changes
\item Comments can be overwritten when a \gdcase{} is reused.
\bxtipp{You can see the comment for a \gdcase{} when you hover over it in the \gdtestcasebrowser{} or the \gdtestsuitebrowser{} or in the search results view.}
\end{enumerate}


\subsection{Deleting \gdsteps{} and \gdcases{} from a \gdcase{}}
\index{Delete!Test Steps}
\index{Delete!Test Cases}
\index{Test Case!Delete}
\index{Test Step!Delete}
\begin{enumerate}
\item Open the \gdtestcaseeditor{} by double-clicking on the \gdcase{} you want to edit in the \gdtestcasebrowser{}.  
\item Right-click on the item to be deleted in the \gdtestcaseeditor{}
 and select 
\bxcaption{Delete} from the context-sensitive menu.  
\item You can also use \bxkey{DELETE} to delete items.  
\item Save the changes in the editor.
\end{enumerate}
