
\textbf{Mac OSX Mountain Lion gatekeeper prevents install4j generated installer from starting}
\begin{itemize}
\item This is caused by a too-restrictive setting on the Mountain Lion gatekeeper security feature.
\item Setting the security level to Mac OSX Lion compatible level resolves the issue.
\end{itemize}

\textbf{Actions: Check selection of entry by index/value only checks one entry}
\begin{itemize}
\item The actions for checking whether an item in a list is selected have been adapted so that they only accept one piece of data, and not comma-separated values as was previously the case.
\item To check whether multiple items are selected, use a data set which contains a list of the items to check. 
\end{itemize}

\textbf{Announcement for next release: removal of deprecated unbound modules and major API change to RC code}
\begin{itemize}
\item In the next release, we will remove the unbound modules in all toolkits that are marked as deprecated. Please ensure that you have replaced any modules marked as deprecated before updating to the first released version in 2013.
\item Due to changes we will be making to our implementation classes for the RC components (actions on components), there will also be major API changes which will affect extensions that have been written. 
\end{itemize}

\textbf{Removed BIRT Reports for Object Mapping Quality}
\begin{itemize}
\item The BIRT reports for monitoring object name quality (\bxname{OMNameQuality} and \bxname{OMNameQualityChart}) have been removed.
\end{itemize}
