% BREDEX LaTeX Template
%  \documentclass is either ``bxreport'' or ``bxarticle''
%                 option is bxpaper
%% \documentclass{bxarticle}
%% % ----------------------------------------------------------------------
%% \begin{document}
%% \title{}
%% \author{}
%% % \author*{Hauptautor}{Liste der Nebenautoren}
%% \maketitle
%% % ----------------------------------------------------------------------
%% \bxversion{0.1}
%% %\bxdocinfo{STATUS}{freigegeben durch}{freigegeben am}{Verteilerliste}
%% \bxdocinfo{DRAFT}{}{}{}
%% % ----------------------------------------------------------------------

%% \end{document}
\index{Test Executor}
\begin{enumerate}
\item You can also enter test executor parameters in an XML configuration file.
\item This saves you typing in the same details each time you start a test.
\item To enter the configuration file path, enter the following command:\\
\bxshell{-c <path to file>}

For example:
\emph{-c ''C:/My Documents/config1.xml''}
\item You can also overwrite parameters contained in the configuration file by entering another parameter directly into the interface. 
\item For example, if your configuration file contains the \gdsuite{} \bxcaption{Suite1}, but you enter \bxshell{-testsuite ''Suite2''} in the command line interface, the \gdsuite{} called \bxcaption{Suite2} will be started, not \bxcaption{Suite1}.
\item To create an XML file:
\begin{enumerate} 
\item Open a text editor of your choice. 
\item Enter the desired parameters as shown in the example:
\footnotesize
\begin{verbatim}
<configuration>
    <project>ExampleProject</project>
    <version>1.0</version>
    <autconfig>local configuration</autconfig>
           OR
    <autid>Adder</autid>
    <dbscheme>embedded</dbscheme>
    <dbuser>sa</dbuser>
    <dbpw></dbpw>
    <server>localhost</server>
    <port>60000</port>
    <language>EN_US</language>
    <testsuite>Suite1</testsuite>
            OR
    <testjob>Job1</testjob>        
    <datadir>C:/Program Files/guidancer/data</datadir>
    <resultdir>C:/Program Files/guidancer/results</resultdir>
</configuration>
\end{verbatim}
\normalsize
\item Save the file as an XML file.
\item This file will be used when you enter the \bxcaption{-c <path to file>} parameter.
\bxtipp{The no-run and quiet mode parameters can only be entered in the command line interface. They cannot be entered in the configuration file.}
\bxtipp{Java Virtual Machine parameters can only be entered in the command line interface. They cannot be entered in the configuration file.}
\end{enumerate}
\item A template configuration file was installed with \app{}. It can be found under:\\
\bxname{InstallationDirectory/examples/scripts}
\end{enumerate}
