\textbf{Selenium update}
\begin{itemize}
\item We have updated the version of Selenium used for HTML tests to 2.39.
\end{itemize}

\textbf{Port number for embedded \gdagent{} changed}
\begin{itemize}
\item The default port number for the embedded \gdagent{} is now 60001.
\item You can change the default port number in the preferences.
\end{itemize}

\textbf{Table view has been removed from the \gdomeditor{}}
\begin{itemize}
\item The table view has been removed from the \gdomeditor{}.
\end{itemize}

\textbf{Problems opening BIRT reports when using IE11}
\begin{itemize}
\item There is a known issue with BIRT reporting that occurs when using Internet Explorer 11. 
\item There is a ticket open in the \gd{} Bugzilla (\url{https://bugzilla.bredex.de/show_bug.cgi?id=1281}) and in the Eclipse Bugzilla (\url{http://eclip.se/422056}) for this. The ticket in the Eclipse Bugzilla documents workarounds.
\end{itemize}

\textbf{Java 1.4 \gdauts{} no longer testable}
\begin{itemize}
\item As of this version, Java 1.4 \gdauts{} are no longer testable with the \ite{}. 
\end{itemize}

\textbf{Changes to the launcher for the \gdagent{}}
\begin{itemize}
\item The \gdagent{} is no longer available under the name \bxshell{autagent-lin} or \bxshell{autagent-sol}.
\item Use the launcher \bxshell{autagent} instead.
\end{itemize}

\textbf{Java 7 tests on Mac}
\begin{itemize}
\item There are still some issues running tests on Mac machines with Java 7. We suggest using Java 6 on Mac machines for the moment.
\end{itemize}

\textbf{Working directory for \ite{} and \gdagent{} on Linux}
\begin{itemize}
\item The \gdagent{} and the \ite{} now  use the current directory as their working directory on Linux systems.
\end{itemize}


\textbf{The \ite{} now uses Java 7}
\begin{itemize}
\item We have updated the version of Java installed with the \ite{} to version 7.
\end{itemize}

\textbf{The installer requires Java 7}
\begin{itemize}
\item You will need Java 7 installed to be able to run the installer.
\end{itemize}

\textbf{iOS 5.0 no longer supported}
\begin{itemize}
\item We no longer support testing on iOS 5.0 \gdauts{}.
\end{itemize}

\textbf{Working with RDP connections on Windows 8}
\begin{itemize}
\item Windows 8 users working with RDP connections for test execution should ensure that they have installed all updates for Windows. 
\end{itemize}

\textbf{Updated the version of EclipseLink used}
\begin{itemize}
\item In this version, we have switched to EclipseLink 2.5.1 and JPA 2.1.0.
\end{itemize}

\textbf{Vista support removed}
\begin{itemize}
\item We no longer execute tests on Vista: the support for Vista has been removed for this version.
\end{itemize}

\textbf{Multi-window mode for HTML testing on Mac OSX}
\begin{itemize}
\item There are known issues with starting \gdauts{} that are using the multi-window mode on Mac OSX, both in Firefox and Safari.
\item We have removed these combinations from our tests.
\end{itemize}
