\index{Chronon!Support for AUTs}

You can configure your \gdaut{} to run with Chronon recording so that you can analyze any errors that occur during your automated test runs. See the section later \bxpref{TasksChrononTools} on analysing the reports for information on the tooling required to do this.

\bxtipp{\jb users: The support for Chronon recording in \gdauts{} is currently only available in the standalone software.}

\subsubsection{Adding Chronon information in the \gdaut{} configuration}
\gdhelpid{autConfigSettingWizardPagePageContextId}{Configuring an AUT}
You can select Chronon as a monitoring agent and configure it in the Expert Settings in the \gdaut{} configuration. 

\begin{enumerate}
\item Open the \gdaut{} configuration dialog from the \gdproject{} properties \bxpref{projectproperties}.
\item Select the \bxname{Expert} configuration. 
\item Choose whether you want to use the integrated Chronon version \bxpref{TasksChrononAUTIntegrated} or a separate Chronon installation (recommended for continuous integration) \bxpref{TasksChrononAUTSeparate}. 
\item You can then enter the configuration details for the monitoring.
\end{enumerate}


\subsubsection{Configuring the integrated Chronon for use with your \gdaut{}}
\gdhelpid{autConfigSettingWizardPagePageContextId}{Configuring an AUT}
\label{TasksChrononAUTIntegrated}
You can use this option if you do not have a separate Chronon installation on your machine. Enter the following configuration details:
\begin{description}
\item [Include patterns:]{Enter a comma-separated list of packages that you want to be covered by the monitoring. The packages must adhere to the patterns as defined in the Chronon documentation, for example \bxshell{com.myorg.**} selects the whole com.myorg namespace. \bxshell{com.myorg.*} selects only classes in the com.myorg package. The documentation for the patterns is located at \\
\href{https://chronon.onconfluence.com/display/DOC/Include+and+Exclude+patterns}{https://chronon.onconfluence.com/display/\\
DOC/Include+and+Exclude+patterns}.\\
 If you enter no patterns, the recording file will be empty.}
\item [Exclude patterns:]{Enter a comma-separated list of packages that you want to be ignored by the monitoring. The packages must adhere to the patterns as defined in the Chronon documentation, for example \bxshell{com.myorg.**} selects the whole com.myorg namespace. \bxshell{com.myorg.*} selects only classes in the com.myorg package. The documentation for the patterns is located at \\
\href{https://chronon.onconfluence.com/display/DOC/Include+and+Exclude+patterns}{https://chronon.onconfluence.com/display/\\
DOC/Include+and+Exclude+patterns}.}
\item [Target directory:]{Enter the path to a directory where the recording files should be written. The \gdaut{} must have write permissions to this place. Any non-existing folders will be automatically created. This target directory and all items it contains are deleted when the \gdaut{} is started or restarted. Once the \gdaut{} is started, the target directory is recreated ready for the next run. This means you must ensure you have copied any relevant files before starting or restarting the \gdaut{}. When the \gdaut{} is stopped after a test, the recording file is written to this target directory. The target directory can be relative to the \gdaut{} working directory, if you have entered one.}
\item [Operating System:]{Enter \bxshell{win}, \bxshell{lin}, \bxshell{sol} or \bxshell{mac} to specify your operating system. }
\item[JRE Architecture:]{Enter \bxshell{32} or \bxshell{64} to specify your architecture. If you have entered \bxshell{mac} as an operating system, you can only enter \bxshell{64}.}
\end{description}

\textbf{Integrated Chronon and continuous integration}\\

Although you could technically use the integrated Chronon with \app{} outside of the \ite{} in Continuous Integration environments, neither BREDEX nor Chronon Systems recommends or will provide support for such cases.

The use of the integrated Chronon for your \gdaut{}  is meant to be used inside of the \ite{}. If you do want to record your tests outside of the \ite{}, you should use a separate Chronon installation as documented in the following section \bxpref{TasksChrononAUTSeparate}. 

Information on the Chronon Systems' Chronon recording server is available here:\\
 \href{http://www.chrononsystems.com/products/chronon-recording-server/}{http://www.chrononsystems.com/products/chronon-recording-server/}\\
and Embedded Chronon:\\
\href{http://www.chrononsystems.com/products/embedded-chronon}{http://www.chrononsystems.com/products/embedded-chronon} \\
 offerings which are explicitly designed for and support such use cases.


\subsubsection{Configuring a separate Chronon installation for use with your \gdaut{}}
\gdhelpid{autConfigSettingWizardPagePageContextId}{Configuring an AUT}
\label{TasksChrononAUTSeparate}

You can use this option if you have a separate Chronon Recording Server installation on your machine. This option is recommended for continuous integration processes.  Enter the following configuration details:

\begin{description}
\item [Java Agent JAR:]{Enter the path to the Chronon recorder JAR you have installed.}
\item [Native Agent File:]{The path to the platform-specific native recorder agent library.}
\item [Config file:]{Enter the absolute path to the configuration file for the recorder. The configuration file has the same setup as a Java properties file. It must contain the following properties:\\
\bxshell{servermode} (set to true)\\
\bxshell{name} (the \gdaut{} name as it will be displayed in the Chronon Recording Server UI)\\
\bxshell{autostartwithconfig} (if you want the recording to start automatically (recommended when working with \app{}), then the recording parameters need to be set in the Chronon application.)\\ 
\bxshell{port} (optional -- if none is entered, 8042 is used.). \\
The documentation for the configuration file is available on the Chronon site:\\
\href{http://chronon.onconfluence.com/\\
display/DOC/Recorder+Configuration+File}{http://chronon.onconfluence.com/\\
display/DOC/Recorder+Configuration+File}}
\end{description}

\bxtipp{You can also refer to the Chronon documentation for information on the required parameters to run your tests with the Recording Server. :\\
\href{http://chronon.onconfluence.com/display/DOC/Recording+outside+Eclipse}{http://chronon.onconfluence.com/display/DOC/Recording+outside+Eclipse}\\}

\subsubsection{Adapting tests to improve data collection}
You should bear the following in mind when using Chronon for recording information in automated tests.\\

\textbf{Performance in the \gdaut{} may be affected}
\begin{itemize}
\item The recordings that Chronon performs are very memory-intensive. For this reason, you may notice performance differences in your \gdaut{}. It may also be necessary to increase the step delay for your tests, and / or add extra synchronization to compensate for the performance differences when Chronon is running. 
\item For these reasons, we do not recommend having Chronon configured as a part of your standard \gdaut{} configuration. Instead, we suggest running tests with Chronon monitoring when needed. 
\item We also strongly suggest ensuring that your \gdaut{} and the machine it is running on have sufficient memory to cope with the increased monitoring activity.
\end{itemize}

\textbf{Stopping or restarting the \gdaut{} will cause the previously recorded information to be lost}
\begin{itemize}
\item The recording files are written when the \gdaut{} is stopped. This means either stopping the \gdaut{} by hand, using the \bxcaption{Stop AUT} button in \app{} or when you use the \bxname{restart} action. 
\item Because of this, we recommend executing individual \gdcases{} (use cases) in \gdsuites{} that you want to analyze with Chronon. You should ensure that any \gdehandlers{} in the \gdsuite{} will not cause the \gdaut{} to restart.
\end{itemize}




\subsubsection{Analyzing the generated reports}
\label{TasksChrononTools}
To analyze the reports generated, you will require the Chronon Time Travelling Debugger from Chronon Systems. \app{} users can download a trial version of this tool. The link to the trial version is provided in the expert \gdaut{} configuration.

Open source projects may contact Chronon Systems for free licenses. 


