%% % $Id: export.tex 10579 2010-03-18 17:40:32Z alexandra $
%% % Local Variables:
%% % ispell-check-comments: nil
%% % Local IspellDict: american
%% % End:
%% % --------------------------------------------------------
%% % User documentation
%% % copyright by BREDEX GmbH 2005
%% % --------------------------------------------------------
%% % this command can be inserted multiple times
%% \gdhelpid{}
%% % 
%% \begin{bxdescription}
%% \end{bxdescription}
%% %
%% \begin{bxsteps}
%% % use the \item command for single steps
%% \end{bxsteps}
%% % change <FILE> to the same filename you are editing
%% \bxinput{Links/<FILE>}
%% %
%% % other usefull commands are
%% %   \bxhint{}        to create a hint
%% %   \bxwarn{}        to describe a warning
\index{Project!Export}
\index{Export!Project}
\index{Export!All}

 You can choose to export the currently opened \gdproject{} \bxpref{exportsingle} or all of the \gdprojects{} in the database \bxpref{exportall}. \gdprojects{} are exported in .xml format so that they can be added to e.g. version control systems. 

\bxtipp{Projects are exported along with all their test result summaries.}

\subsubsection{Exporting the currently opened \gdproject{}}
\label{exportsingle}
\begin{enumerate}
\item To export a single \gdproject{} from the database, the \gdproject{} you want to export must be open.   
\item Select:\\
\bxmenu{Project}{Export}{}. 
\item Choose the location to save your \gdproject{}, and the name you want to save it under. 
\item Click \bxcaption{OK}. 
\item The \gdproject{} (including the test result summaries \bxpref{TestResSumView}) will be saved as an .xml file. 

\bxtipp{When you export a single \gdproject{}, only the currently opened version is exported.}

\end{enumerate}
\subsubsection{Exporting all of the \gdprojects{} from the database}
\label{exportall}
\begin{enumerate}
\item Select:\\
\bxmenu{Project}{Export all}{}. 
\item Choose or create a folder where you want the \gdprojects{} to be stored. 
\item Click \bxcaption{OK}. 
\item The \gdprojects{} (including the test result summaries \bxpref{TestResSumView}) will be saved as .xml files. 
\bxtipp{When you export all \gdprojects{}, all versions of each \gdproject{} are exported.}

\end{enumerate}

